Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 dropping.tex
Change "overheads" to "overhead".

In this section, we present our hardware architecture that enables partial
monitoring for adjustable overheads. Section~\ref{sec:dropping.baseline} first
describes our baseline model for run-time monitoring while the rest of the
section describes our design.

@@

Our goal is to drop some monitoring operations in order to reduce the overheads
of run-time monitoring. This dropping can affect the functionality of the
monitoring schemes. There are three possible outcomes for dropping a
monitoring operation. The first is that there is no difference in operation
from the original execution. For example, if we drop line 3b from our array
bounds check example (Figure~\ref{fig:dropping.example_full}), then the
check on accessing {\tt x+12} is skipped. However, this is a valid access and so
skipping the check does not change anything.

On the other hand, if the monitoring for accessing memory location {\tt y+12} on
line 4 is skipped, then
a false negative occurs. Originally, the monitor would catch this access as an
out-of-bounds access and raise an error. However, if the monitoring operation
for this is dropped, then the error is not detected. This reflects the trade-off that
we make in order to reduce overheads. Instead of either 100\% coverage
with all the associated overheads or no coverage and no overheads, we 
enable middle points of partial coverage with some fraction of the full
overheads.

The final possible outcome of dropping a monitoring operation is a false positive. 
For example, suppose the monitoring for
line 1 is dropped, causing the bound information for pointer {\tt x} to never
be set. The result is that when the access using {\tt x} is checked on line 3b,
an error will be raised. This creates a false positive where an error is
incorrectly raised. Although false negatives are part of the trade-off we make
to reduce overheads, we need to prevent false positives.

>>>>

In this section, we present our hardware architecture that enables partial
monitoring for adjustable overhead. Section~\ref{sec:dropping.baseline} first
describes our baseline model for run-time monitoring while the rest of the
section describes our design.

@@

Our goal is to drop some monitoring operations in order to reduce the overhead
of run-time monitoring. This dropping can affect the functionality of the
monitoring schemes. There are three possible outcomes for dropping a
monitoring operation. The first is that there is no difference in operation
from the original execution. For example, if we drop line 3b from our array
bounds check example (Figure~\ref{fig:dropping.example_full}), then the
check on accessing {\tt x+12} is skipped. However, this is a valid access and so
skipping the check does not change anything.

On the other hand, if the monitoring for accessing memory location {\tt y+12} on
line 4 is skipped, then
a false negative occurs. Originally, the monitor would catch this access as an
out-of-bounds access and raise an error. However, if the monitoring operation
for this is dropped, then the error is not detected. This reflects the trade-off that
we make in order to reduce overhead. Instead of either 100\% coverage
with all the associated overhead or no coverage and no overhead, we 
enable middle points of partial coverage with some fraction of the full
overhead.

The final possible outcome of dropping a monitoring operation is a false positive. 
For example, suppose the monitoring for
line 1 is dropped, causing the bound information for pointer {\tt x} to never
be set. The result is that when the access using {\tt x} is checked on line 3b,
an error will be raised. This creates a false positive where an error is
incorrectly raised. Although false negatives are part of the trade-off we make
to reduce overhead, we need to prevent false positives.

### 2015-01-05 evaluation.tex
Change "overheads" to "overhead".

\subsection{Baseline Monitoring Overheads}

@@

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    %\includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0.1in]{figs/data_filtering.pdf}
    \includegraphics[width=\columnwidth]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with null metadata filtering.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 2.6-9.8x with an average of 5.7x.
For BC, normalized execution
are 2.7x on average and range from 1.02x to 13.6x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 1.6-9.5x with an average of 5.8x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.04-1.29x after null metadata filtering and the average
overhead observed is 1.13x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds checking as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. This may
not necessarily be true for actual errors/attacks and so the reported coverage
may not be the same as the probability of detecting actual errors/attacks.
However, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target (10\% slowdown), array bounds check still
achieves over 80\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing a certain level of monitoring coverage without
introducing overheads. The second effect is that there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring.
With a 2x overhead target, UMC achieves 22\% monitoring coverage on average and with a 4x overhead target, this increases to 49\%.
%We see that
%with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
%By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
%average. 
Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With only a 1.01x overhead, LS achieves 30\% coverage on average. This increases to
71\% coverage with a 1.1x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.
Note that the overheads shown are the target overhead. In some cases, a high
overhead target is needed in order to achieve 100\% coverage. For example, for
{\tt mcf} with UMC monitoring, a 12x overhead target is needed to achieve 100\%
coverage while the overheads of performing monitoring in full were 2.6x (see
Figure~\ref{fig:evaluation.filtering}. This is due to the fact that we
accumulate slack gradually and so bursty monitoring events may require a higher
overhead target in order for all monitoring to be performed. However, the
actual overheads seen are in-line with the overhead of performing monitoring
without dropping (e.g., 2.6x for {\tt mcf} with UMC monitoring at a 12x
overhead target).

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overheads. We see that
with a 1.1x overhead, a max error of 9\% is observed across the benchmarks and the
average error across instruction types and benchmarks is 3\%.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.9x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-2.0x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing 45\% coverage.

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 2.0x for UMC and 1.5x for BC.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. For most benchmarks, we see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of short, independent monitoring dependence chains. Source-only dropping
causes overshoot of the overhead target for {\tt hmmer} and {\tt h264ref}.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping while still closely matching the overhead target. For example, {\tt perlbench} shows a 10\% increase in coverage and {\tt libquantum} shows an 18\% increase in coverage by using source-only dropping. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only dropping fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with overhead differences over 100\% for {\tt bzip2}, {\tt hmmer}, and {\tt h264ref}.
Since only infrequently occurring array allocations are considered as source events for BC, it can be 
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

@@

One application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check using
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 500 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 6\% increase in coverage with only eight runs.
With more runs, source-only dropping should be able to
reach 100\% code coverage.

>>>>

\subsection{Baseline Monitoring Overhead}

@@

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    %\includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0.1in]{figs/data_filtering.pdf}
    \includegraphics[width=\columnwidth]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overhead with null metadata filtering.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 2.6-9.8x with an average of 5.7x.
For BC, normalized execution
are 2.7x on average and range from 1.02x to 13.6x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overhead. IMP shows normalized
execution times of 1.6-9.5x with an average of 5.8x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.04-1.29x after null metadata filtering and the average
overhead observed is 1.13x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overhead.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds checking as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. This may
not necessarily be true for actual errors/attacks and so the reported coverage
may not be the same as the probability of detecting actual errors/attacks.
However, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target (10\% slowdown), array bounds check still
achieves over 80\% monitoring coverage on average. The high coverage
achieved with such low overhead is due to two main effects.  The first is that
monitoring can be done in parallel, providing a certain level of monitoring coverage without
introducing overhead. The second effect is that there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overhead without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring.
With a 2x overhead target, UMC achieves 22\% monitoring coverage on average and with a 4x overhead target, this increases to 49\%.
%We see that
%with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
%By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
%average. 
Even higher coverage can be achieved by allowing higher overhead.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With only a 1.01x overhead, LS achieves 30\% coverage on average. This increases to
71\% coverage with a 1.1x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.
Note that the overheads shown are the target overhead. In some cases, a high
overhead target is needed in order to achieve 100\% coverage. For example, for
{\tt mcf} with UMC monitoring, a 12x overhead target is needed to achieve 100\%
coverage while the overheads of performing monitoring in full were 2.6x (see
Figure~\ref{fig:evaluation.filtering}. This is due to the fact that we
accumulate slack gradually and so bursty monitoring events may require a higher
overhead target in order for all monitoring to be performed. However, the
actual overheads seen are in-line with the overhead of performing monitoring
without dropping (e.g., 2.6x for {\tt mcf} with UMC monitoring at a 12x
overhead target).

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overhead. We see that
with a 1.1x overhead, a max error of 9\% is observed across the benchmarks and the
average error across instruction types and benchmarks is 3\%.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.9x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-2.0x. We see that partial
monitoring can allow the overhead of such a system to be pushed below 10\%
while still providing 45\% coverage.

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 2.0x for UMC and 1.5x for BC.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overhead for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. For most benchmarks, we see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of short, independent monitoring dependence chains. Source-only dropping
causes overshoot of the overhead target for {\tt hmmer} and {\tt h264ref}.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping while still closely matching the overhead target. For example, {\tt perlbench} shows a 10\% increase in coverage and {\tt libquantum} shows an 18\% increase in coverage by using source-only dropping. This is due
to the fact that some of the overhead of monitoring for unrestricted dropping
is being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only dropping fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with overhead differences over 100\% for {\tt bzip2}, {\tt hmmer}, and {\tt h264ref}.
Since only infrequently occurring array allocations are considered as source events for BC, it can be 
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that it is running with
higher overhead.

@@

One application of partial monitoring with low overhead is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overhead across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check using
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 500 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 6\% increase in coverage with only eight runs.
With more runs, source-only dropping should be able to
reach 100\% code coverage.

### 2015-01-05 introduction.tex
Change "overheads" to "overhead".

Previous studies have explored various design points in terms of efficiency,
flexibility, and hardware costs for implementing run-time monitors. Custom
hardware designs that target a single or narrow-range of monitors have been
shown to have low performance overheads. On the other hand, flexible systems
that support a range of monitors have shown much higher overheads. In this
paper, we explore a new trade-off dimension for run-time monitor designs. We
propose to enable low overhead monitors without sacrificing flexibility by
using partial monitoring. In essence, this enables a trade-off between overheads and
monitoring coverage or accuracy.

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be useful in many scenarios.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overheads are too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for debugging purposes
especially in the context of sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positives, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and increasing the monitoring
coverage.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine can enable null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

The main contributions of this paper are summarized as follows:
\begin{itemize}
  \item We present a hardware architecture using a dataflow tracking engine to
  efficiently enable partial monitoring while preventing false positives. This
  hardware architecture is designed to be generally applicable to a wide-range
  of run-time monitoring techniques and monitor implementations.
  \item We investigate multiple policies on when and which operations to drop 
  for partial monitoring, and show the trade-offs in the design space.
  \item We extend the dataflow engine to enable filtering null metadata to
  reduce overheads.
\end{itemize}

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show average slowdowns of 1.1-5.8x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for the monitors which showed over 2x
average overheads, slowdown could be cut down to 1.5x while still achieving a
coverage of 14-85\% on average.

>>>>

Previous studies have explored various design points in terms of efficiency,
flexibility, and hardware costs for implementing run-time monitors. Custom
hardware designs that target a single or narrow-range of monitors have been
shown to have low performance overheads. On the other hand, flexible systems
that support a range of monitors have shown much higher overheads. In this
paper, we explore a new trade-off dimension for run-time monitor designs. We
propose to enable low overhead monitors without sacrificing flexibility by
using partial monitoring. In essence, this enables a trade-off between overhead and
monitoring coverage or accuracy.

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be useful in many scenarios.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overhead is too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for debugging purposes
especially in the context of sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.

% Adjustable overhead
Partial monitoring with adjustable overhead is achieved by dynamically
dropping monitoring operations when the overhead exceeds a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positives, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and increasing the monitoring
coverage.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine can enable null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

The main contributions of this paper are summarized as follows:
\begin{itemize}
  \item We present a hardware architecture using a dataflow tracking engine to
  efficiently enable partial monitoring while preventing false positives. This
  hardware architecture is designed to be generally applicable to a wide-range
  of run-time monitoring techniques and monitor implementations.
  \item We investigate multiple policies on when and which operations to drop 
  for partial monitoring, and show the trade-offs in the design space.
  \item We extend the dataflow engine to enable filtering null metadata to
  reduce overhead.
\end{itemize}

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show average slowdowns of 1.1-5.8x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overhead. For example, for the monitors which showed over 2x
average overhead, slowdown could be cut down to 1.5x while still achieving a
coverage of 14-85\% on average.

### 2015-01-05 monitoring.tex
Change "overheads" to "overhead".

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some of the representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs between efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{nagarajan-interact08, lift-micro06,
purify-usenix92, taintcheck-ndsss05} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overheads are also unpredictable because they
depend heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.

>>>>

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some of the representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs between efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{nagarajan-interact08, lift-micro06,
purify-usenix92, taintcheck-ndsss05} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overhead is also unpredictable because it
depends heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.
